Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2019-11-20 paper2_JNLS/paper.tex
NM

	As diagrammed in Fig.~\ref{ExpDiagStats}(a), the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by plexiglass paddle at one end \cite{bolles2019}. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC) created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since the dampener minimizes backscatter, the waves in this experiment propagate primarily in one direction, from left to right in Fig.~\ref{ExpDiagStats}(a).

@@

	Figure \ref{ExpSpatialStats} shows how these statistics vary in the vicinity of the ADC, located at $x = 0$, for both displacement and slope. First, the standard deviation of displacement, $\etastd$, gives the coarsest possible estimate for the amplitude of waves. Figure \ref{ExpSpatialStats}(a) shows that while $\etastd$ increases with driving amplitude, it remains relatively uniform in space for each individual experiment, indicating that the overall amplitude of the wave train is not significantly altered by the presence of the ADC. The skewness and kurtosis, however, respond strongly to the ADC as long as the amplitude is sufficiently high. As seen in \ref{ExpSpatialStats}(b)--(c), both the skewness and kurtosis are relatively small upstream of the ADC, indicating nearly Gaussian statistics, but then increase dramatically downstream and reach a peak near $x = 15$ cm. Remarkably, the location of the peak is the same for skewness and kurtosis and appears insensitive to driving amplitude. The maximum values of skewness and kurtosis (roughly 0.9 and 0.7 respectively) seen in the figure indicate a significant departure from Gaussian statistics, as is constant with the histogram in Fig.~\ref{ExpDiagStats}(e). \boetal found that, once a threshold driving amplitude is exceeded (roughly $\Dphi = 0.5^{\circ}$), the displacement statistics in this anomalous region are robustly described by the gamma distribution. We note that we have gathered data for 15 different driving amplitudes, but only display 6 in Fig.~\ref{ExpSpatialStats} to avoid clutter.

@@

We now introduce the theoretical framework that will be used to understand and quantify the experimental observations. This framework is based on a Galerkin truncation of the variable-depth Korteweg–de Vries (KdV) equation. The KdV equation is a well established model for describing the propagation of unidirectional, shallow-water waves, and it accounts for weak nonlinearity and weak dispersion over long timescales and large spatial scales. We will perform Galerkin truncation of KdV to obtain a finite-dimensional dynamical system that exhibits weak turbulence. We outline the Hamiltonian structure of both the continuous KdV and the truncated system. This structure is exploited to obtain invariant measures of the underlying dynamics and, ultimately, to rationalize the experimental findings on anomalous wave statistics triggered by an ADC.

@@

We consider the surface displacement $\eta(x,t)$ of unidirectional, shallow-water waves in a reference frame moving with the characteristic wave speed, $\xi = x - ct$. Here, $c = \sqrt{g \depth}$ is leading-order approximation to the wave speed (i.e.~from linear theory), where $g$ is gravity and $\depth$ is the local depth.
The leading-order dynamics are corrected to first order in small amplitude by the Korteweg–de Vries equation (KdV), which in dimensional form is given by \cite{whitham2011linear}
\begin{equation}
\label{KdV}
\eta_t + \frac{3 c}{2 \depth} \eta \eta_{\xi} + \frac{c \depth^2}{6} \eta_{\xi \xi \xi} = 0
\end{equation}
% Given by Whitham on p. 461, Eq. 13.98
Motivated by the experiments, we consider waves that originate from a region of constant depth, encounter an abrupt depth change, and continue into another region of constant depth. Thus, depth will be piecewise constant
\begin{align}
\depth = 
\begin{cases}
\dup \quad \mbox{if } x<0 \\
\ddn \quad \mbox{if } x>0
\end{cases}
\end{align}
Most often, we will consider waves moving into shallower depth, so that $\dup > \ddn$. Throughout this paper, we will use the subscript `-' to represent upstream variables and `+' for downstream variables.

@@

In this section, the variable-depth KdV equation \eqref{KdV} will be recast into a dimensionless form that is chosen for convenience in working with the statistical-mechanics framework from \maetal \cite{majda2019}. Since the choice of normalization is not unique, it is instructive to first introduce a generic normalization to facilitate comparison with other possible choices. To this end, we consider characteristic scales, $\ampscale, \lengthscale, \timescale$ for the wave amplitude, longitudinal length, and time respectively, which can remain unspecified for the moment. We introduce the dimensionless variables
\begin{align}
&u = \eta / \ampscale
&&\mbox{\em dimensionless surface displacement} \\
&\tilde{x} = (x-ct) / \lengthscale
&&\mbox{\em dimensionless position (in moving frame)} \\
&\tilde{t} = t / \timescale
&&\mbox{\em dimensionless time}
\end{align}
Recasting \eqref{KdV} in terms of these variables gives the generic dimensionless KdV equation:
\begin{equation}
u_t + \frac{3}{2} \left( \frac{c \timescale \ampscale}{\lengthscale \depth} \right) u u_x 
+ \frac{1}{6} \left( \frac{c \timescale \depth^2}{\lengthscale^3} \right) u_{xxx} = 0
\end{equation}
We have dropped the tilde notation above for simplicity and will henceforth use tildes only in cases of possible ambiguity.

@@

	Lastly, regarding the characteristic timescale $\timescale$, the most basic timescale in the experiments is simply $\freqp^{-1}$, i.e.~the period of waves passing a fixed reference point. Of course, the leading-order behavior in shallow water is simply wave propagation with uniform speed $c$, i.e.~no dispersion. The KdV equation provides the first correction to this behavior and describes dynamics that evolve over longer timescales. Hence we have rescaled $\freqp^{-1}$ by the factor $N \lam/(2 \pi \depth) \gg 1$, which provides a suitably long timescale in line with previous normalizations \cite{johnson1997modern}. The scales $\lengthscale = \lengthscale_{\pm}$ and $\timescale = \timescale_{\pm}$ change value across the ADC, which is important to note when comparing the theory against experimental measurements.

@@

The variable-depth KdV \eqref{dimlessKdV}, though not Hamiltonian throughout the entire domain, admits a Hamiltonian structure on each side of the ADC. Indeed, \eqref{dimlessKdV} can be expressed as
\begin{align}
\label{HamStruct}
\partial_t{u} = \sympJ \vard{\Hupdn}{u}
\end{align}
where $\sympJ = \pdi{}{x}$ is the symplectic operator and $\Ham = \Hupdn$ is the Hamiltonian, which takes different forms on either side of the ADC. It is convenient to decompose the Hamiltonian into a so-called cubic and quadratic component, given respectively by
\begin{align}
\label{H3H2}
\Hthree = \frac{1}{6} \int_{-\pi}^{\pi} u^3 \dx	\, , \qquad
\Htwo = \frac{1}{2} \int_{-\pi}^{\pi} u_x^2 \dx	\, .
\end{align}
Then the Hamiltonian can be expressed as
\begin{equation}
\label{Hamiltonian}
\Hupdn = C_2 \dratupdn^{1/2} \, \Htwo - C_3 \dratupdn^{-3/2} \, \Hthree
\end{equation}
where $\drat = \dratupdn$ changes value across the ADC. More explicitly, substituting \eqref{dratpw} gives the separate upstream and downstream Hamiltonians as
\begin{align}
&\Hup = C_2 \, \Htwo - C_3 \, \Hthree 						&& \text{for } t<0 \\
&\Hdn = C_2 \dratdn^{1/2} \, \Htwo - C_3 \dratdn^{-3/2} \, \Hthree	&& \text{for } t>0
\end{align}
As seen in \eqref{H3H2}, the cubic component, $\Hthree$, represents the skewness of the wave-field, while the quadratic component, $\Htwo$, represents the energy of the surface slope. The sign difference between the two \eqref{Hamiltonian} thus represents a competition between wave skewness and slope energy. In particular, the role played by the slope energy is the motivating factor for the new experimental measurements on surface {\em slope} statistics that are reported in this paper.

@@

	To compute the transfer function, we use a weighted random-sampling strategy. That is, we first sample the Fourier coefficients $\uhvec = \left\{ \uhat_{k}\right\}_{k=0}^{\Lambda}$ from a uniform distribution on the unit hypersphere $\En = 1$. The uniform sampling is achieved by first sampling from a isotropic Gaussian distribution and then normalizing to project onto the hypersphere \cite{abramov2003}. These samples are then weighted by the appropriate Gibbs measure \eqref{Gibbs} to compute the expectations needed in the statistical matching condition \eqref{statmatch}. That is, for an arbitrary quantity $Q$, the ensemble expectation corresponding to Hamiltonian $\Ham$ and inverse temperature $\theta$ is numerically approximated as
\begin{equation}
\label{weightmean}
\mean{Q}_{\theta} = \frac{\sumsamp Q_i \exp(-\theta \Ham_i)} {\sumsamp \exp(-\theta \Ham_i)}
\end{equation}
where $\Nsamp$ is the number of samples. Then, enforcing the statistical matching condition \eqref{statmatch} becomes a root-finding problem for the function
\begin{equation}
\label{rooteq}
\Fth(\thdn) =  \mean{\Hdn}_{\thdn} - \mean{\Hdn}_{\thup} = 0
\end{equation}
Recall that we consider $\thup$ as given, so that $\mean{\Hdn}_{\thup}$ is a constant that can be computed straightaway from \eqref{weightmean}. We then use the secant method with respect to the variable $\thdn$ to find a root of $\Fth(\thdn)$ to the desired tolerance.

@@

	We note that the experiments discussed here preceded the development of the theory, and hence had no intent of mimicking a Gibbs measure in the wave forcing. We expect that if the experimental forcing were designed to mimic the Gibbs measure, in particular the spectral decay, then it would be more straightforward to assign a value to the model parameter $\lamfac$. We, however, leave that task for future research due to the significant cost of performing an entirely new set of experiments compared to the relative ease and great value in re-analyzing existing experimental measurements in light of the new theoretical developments.

@@

At this point, all parameters that appear in the theoretical model have been linked directly to experimental parameters with the exception of the inverse temperature of the incoming flow, $\thup$.
Our strategy is to use the outgoing skewness as the main diagnostic to determine a realistic range for $\thup$. That is, for an input $\thup$, the downstream inverse temperature $\thdn$ is determined by \eqref{statmatch}, which ultimately sets the skewness of the outgoing wave-field.

@@

	We now aim to compare the wave statistics measured in experiments against those that emerge from the TKdV theory. Throughout, we will focus on the representative set of experiments detailed in Table \ref{paramtable}, in which the peak downstream skewness was measured to be 0.83. 
With $(\Lambda, \lamfac) = (16, 8)$ fixed, Fig.~\ref{transfig}(c) indicates $\thup = 20$ as a reasonable value to attain the desired skewness. We thus run the deterministic TKdV simulations with these model parameters and with $\epsup$, $\delup$, and $\dratdn$ set to the representative values in Table \ref{paramtable}. We run the simulations to a sufficiently long dimensionless time of $t_{f} = 10$, with $dt = 5 \times 10^{-4}$ and with $10^3$ trajectories sampled from the upstream Gibbs measure $\Gup$.

@@

We now discuss arguably the most novel single result of the manuscript. In the recent theoretical study, \maetal derived an explicit formula for the outgoing wave-field skewness in terms of the system parameters \cite{majda2019}. More specifically, this formula relates the downstream skewness of surface displacement $\skw(\eta)$ to the change in slope variance $\var(\eta_x)$. Here, we recap the derivation of this formula and then test the prediction against new, direct experimental measurements.

@@

Inserting \eqref{H3convert} and \eqref{H2convert} into \eqref{H3H2ratio}, and using the definitions of $C_2$ and $C_3$ from \eqref{C3C2}, gives the remarkably explicit formula
\begin{equation}
\label{SkewPred}
\frac{\skwdn(\eta)} {\vardn(\eta_x) - \varup(\eta_x)} = \frac{1}{3} \epsup^{-3} \dratdn^3 
%= \frac{1}{3} \left( \frac{\ddn}{\etastd} \right)^3
\end{equation}
This formula links the skewness of the outgoing wave field to the change in the variance of surface slope. In particular, it predicts their ratio to scale as the {\em inverse cube of wave amplitude}, $\epsup^{-3}$, and the {\em cube of the depth ratio}, $\dratdn^3$. It is a rather unexpected relationship, as it would have been difficult to anticipate that the displacement skewness and slope variance, among all possibly variable combinations, are so intimately related.

 % Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/SkewRat.pdf}
\caption{
Experimental confirmation of the explicit formula for outgoing skewness \eqref{SkewPred}.
(a)--(b) Spatial variation of $\skw(\eta)$ and $\var(\eta_x)$ for several different amplitudes. The maximum of $\skw(\eta)$ and the minimum of $\var(\eta_x)$ each occur at a location that is insensitive to amplitude, $x = $15 cm (blue) and -9 cm (green) respectively, which are chosen as the representative locations to evaluate \eqref{SkewPred}.
(c) Measurements of the ratio $\skw(\eta) / \Delta \var(\eta_x)$ from 15 different experiments plotted against the dimensionless wave amplitude $\epsup$. For sufficiently large amplitude, the measurements fit closely with the $\epsup^{-3}$ prediction from \eqref{SkewPred}.
}
\label{SkewRat}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 %New experimental measurements guided by theory

>>>>

	As diagrammed in Fig.~\ref{ExpDiagStats}(a), the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by a plexiglass paddle at one end \cite{bolles2019}. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC) created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since the dampener minimizes backscatter, the waves in this experiment propagate primarily in one direction, from left to right in Fig.~\ref{ExpDiagStats}(a).

@@

	Figure \ref{ExpSpatialStats} shows how these statistics vary in the vicinity of the ADC, located at $x = 0$, for both displacement and slope. First, the standard deviation of displacement, $\etastd$, gives the coarsest possible estimate for the amplitude of waves. Figure \ref{ExpSpatialStats}(a) shows that while $\etastd$ increases with driving amplitude, it remains relatively uniform in space for each individual experiment, indicating that the overall amplitude of the wave train is not significantly altered by the presence of the ADC. The skewness and kurtosis, however, respond strongly to the ADC as long as the amplitude is sufficiently high. As seen in \ref{ExpSpatialStats}(b)--(c), both the skewness and kurtosis are relatively small upstream of the ADC, indicating nearly Gaussian statistics, but then increase dramatically downstream and reach a peak near $x = 15$ cm. Interestingly, the location of the peak is the same for skewness and kurtosis and appears insensitive to driving amplitude. The maximum values of skewness and kurtosis (roughly 0.9 and 0.7 respectively) seen in the figure indicate a significant departure from Gaussian statistics, as is constant with the histogram in Fig.~\ref{ExpDiagStats}(e). \boetal found that, once a threshold driving amplitude is exceeded (roughly $\Dphi = 0.5^{\circ}$), the displacement statistics in this anomalous region are robustly described by the gamma distribution across all of the experiments. We note that we have gathered data for 15 different driving amplitudes, but only display 6 in Fig.~\ref{ExpSpatialStats} to avoid clutter.

@@

We now introduce the theoretical framework that will be used to understand and quantify the experimental observations. This framework is based on a Galerkin truncation of the variable-depth Korteweg–de Vries (KdV) equation. The KdV equation is a well established model for describing the propagation of unidirectional, shallow-water waves, accounting for weak nonlinearity and weak dispersion over long timescales and large spatial scales. We will perform Galerkin truncation of KdV to obtain a finite-dimensional dynamical system that exhibits weak turbulence. We outline the Hamiltonian structure of both the traditional KdV and the truncated systems. This structure is exploited to obtain invariant measures of the underlying dynamics and, ultimately, to rationalize the experimental findings on anomalous wave statistics triggered by an ADC.

@@

We consider the surface displacement $\eta(x,t)$ of unidirectional, shallow-water waves in a reference frame moving with the characteristic wave speed, $\xi = x - ct$. Here, $c = \sqrt{g \depth}$ is leading-order approximation to the wave speed (i.e.~from linear theory), where $g$ is gravity and $\depth$ is the local depth.
The leading-order dynamics are corrected to first order in small amplitude by the Korteweg–de Vries equation (KdV), which in dimensional form is given by \cite{whitham2011linear}
\begin{equation}
\label{KdV}
\eta_t + \frac{3 c}{2 \depth} \eta \eta_{\xi} + \frac{c \depth^2}{6} \eta_{\xi \xi \xi} = 0
\end{equation}
% Given by Whitham on p. 461, Eq. 13.98
Motivated by the experiments, we consider waves that originate from a region of constant depth, encounter an abrupt depth change, and continue into another region of constant depth. Thus, depth will be piecewise constant
\begin{align}
\depth = 
\begin{cases}
\dup \quad \mbox{if } x<0 \\
\ddn \quad \mbox{if } x>0
\end{cases}
\end{align}
Most often, we consider waves moving into shallower depth, so that $\dup > \ddn$. Throughout this paper, we use the subscript `-' to represent upstream variables and `+' for downstream variables.

@@

In this section, the variable-depth KdV equation \eqref{KdV} will be recast into a dimensionless form that is chosen for convenience in working with the statistical-mechanics framework of \maetal \cite{majda2019}. Since the choice of normalization is not unique, it is instructive to first introduce a generic normalization to facilitate comparison with other possible choices. To this end, we consider characteristic scales, $\ampscale, \lengthscale, \timescale$ for the wave amplitude, longitudinal length, and time respectively, which can remain unspecified for the moment. We introduce the dimensionless variables
\begin{align}
&u = \eta / \ampscale
&&\mbox{\em dimensionless surface displacement} \\
&\tilde{x} = (x-ct) / \lengthscale
&&\mbox{\em dimensionless position (in moving frame)} \\
&\tilde{t} = t / \timescale
&&\mbox{\em dimensionless time}
\end{align}
Recasting \eqref{KdV} in terms of these variables gives the generic dimensionless KdV equation:
\begin{equation}
u_t + \frac{3}{2} \left( \frac{c \timescale \ampscale}{\lengthscale \depth} \right) u u_x 
+ \frac{1}{6} \left( \frac{c \timescale \depth^2}{\lengthscale^3} \right) u_{xxx} = 0
\end{equation}
We have dropped the tilde notation above for simplicity and will henceforth use tildes only in cases of possible ambiguity.

@@

	Lastly, regarding the characteristic timescale $\timescale$, the most basic timescale in the experiments is simply $\freqp^{-1}$, i.e.~the period of waves passing a fixed reference point. Of course, the leading-order behavior in shallow water is simply wave propagation with uniform speed $c$, i.e.~no dispersion. The KdV equation provides the first correction to this behavior and describes dynamics that evolve over longer timescales. Hence we have rescaled $\freqp^{-1}$ by the factor $N \lam/(2 \pi \depth) \gg 1$, which provides a suitably long timescale in line with other normalizations \cite{johnson1997modern}. The scales $\lengthscale = \lengthscale_{\pm}$ and $\timescale = \timescale_{\pm}$ change value across the ADC, which is important to note when comparing the theory against experimental measurements.

@@

The variable-depth KdV \eqref{dimlessKdV}, though not Hamiltonian throughout the entire domain, admits a Hamiltonian structure on each side of the ADC. Indeed, \eqref{dimlessKdV} can be expressed as
\begin{align}
\label{HamStruct}
\partial_t{u} = \sympJ \vard{\Hupdn}{u}
\end{align}
where $\sympJ = \pdi{}{x}$ is the symplectic operator and $\Ham = \Hupdn$ is the Hamiltonian, which takes different forms on either side of the ADC. It is convenient to decompose the Hamiltonian into a so-called cubic and quadratic component, given respectively by
\begin{align}
\label{H3H2}
\Hthree = \frac{1}{6} \int_{-\pi}^{\pi} u^3 \dx	\, , \qquad
\Htwo = \frac{1}{2} \int_{-\pi}^{\pi} u_x^2 \dx	\, .
\end{align}
Then the Hamiltonian can be expressed as
\begin{equation}
\label{Hamiltonian}
\Hupdn = C_2 \dratupdn^{1/2} \, \Htwo - C_3 \dratupdn^{-3/2} \, \Hthree
\end{equation}
where $\drat = \dratupdn$ changes value across the ADC. More explicitly, substituting \eqref{dratpw} gives the separate upstream and downstream Hamiltonians as
\begin{align}
&\Hup = C_2 \, \Htwo - C_3 \, \Hthree 						&& \text{for } t<0 \\
&\Hdn = C_2 \dratdn^{1/2} \, \Htwo - C_3 \dratdn^{-3/2} \, \Hthree	&& \text{for } t>0
\end{align}
As seen in \eqref{H3H2}, the cubic component, $\Hthree$, represents the skewness of the wave-field, while the quadratic component, $\Htwo$, represents the energy of the surface slope. The sign difference between the two in \eqref{Hamiltonian} thus represents a competition between wave skewness and slope energy. In particular, the appearance of the slope energy in the theory motivated the new experimental measurements on surface {\em slope} statistics reported in this paper.

@@

%----------------------------------------------------------------------------%
% Transfer
%----------------------------------------------------------------------------%
\subsection{Numerical computation of the transfer function}

	To compute the transfer function, we use a weighted random-sampling strategy. That is, we first sample the Fourier coefficients $\uhvec = \left\{ \uhat_{k}\right\}_{k=0}^{\Lambda}$ from a uniform distribution on the unit hypersphere $\En = 1$. The uniform sampling is achieved by first sampling from an isotropic Gaussian distribution and then normalizing to project onto the hypersphere \cite{abramov2003}. These samples are then weighted by the appropriate Gibbs measure \eqref{Gibbs} to compute the expectations needed in the statistical matching condition \eqref{statmatch}. That is, for an arbitrary quantity $Q$, the ensemble expectation corresponding to Hamiltonian $\Ham$ and inverse temperature $\theta$ is numerically approximated as
\begin{equation}
\label{weightmean}
\mean{Q}_{\theta} = \frac{\sumsamp Q_i \exp(-\theta \Ham_i)} {\sumsamp \exp(-\theta \Ham_i)}
\end{equation}
where $\Nsamp$ is the number of samples. Then, enforcing the statistical matching condition \eqref{statmatch} becomes a root-finding problem for the function
\begin{equation}
\label{rooteq}
\Fth(\thdn) =  \mean{\Hdn}_{\thdn} - \mean{\Hdn}_{\thup} = 0
\end{equation}
Recall that we consider $\thup$ as given, so that $\mean{\Hdn}_{\thup}$ is a constant that can be computed straightaway from \eqref{weightmean}. We then use the secant method with respect to the variable $\thdn$ to find a root of $\Fth(\thdn)$ to the desired tolerance.

@@

	We note that the experiments discussed here preceded the development of the theory, and hence had no intent of mimicking a Gibbs measure in the wave forcing. We expect that if the experimental forcing were designed to mimic the Gibbs measure, in particular the precise spectral decay, then it would be more straightforward to assign a value to the model parameter $\lamfac$. We, however, leave that task for future research due to the significant cost of performing an entirely new set of experiments compared to the relative ease and great value in re-analyzing existing experimental data in light of the new theoretical developments.

@@

At this point, all parameters appearing in the theoretical model have been linked directly to experimental parameters with the exception of the inverse temperature of the incoming flow, $\thup$.
Our strategy is to use the outgoing skewness as the main diagnostic to determine a realistic range for $\thup$. That is, for an input $\thup$, the downstream inverse temperature $\thdn$ is determined by \eqref{statmatch}, which ultimately sets the skewness of the outgoing wave-field.

@@

	We now aim to compare the wave statistics measured in experiments against those that emerge from the TKdV theory. Throughout, we will focus on the representative set of experiments detailed in Table \ref{paramtable}, in which the peak downstream skewness was measured to be 0.83. 
With $(\Lambda, \lamfac) = (16, 8)$ fixed, Fig.~\ref{transfig}(c) indicates $\thup = 20$ as a reasonable value to attain the desired skewness. We thus run the deterministic TKdV simulations with these model parameters and with $\epsup$, $\delup$, and $\dratdn$ set to the representative values in Table \ref{paramtable}. We run the simulations to a sufficiently long dimensionless time of $t_{f} = 10$, with $dt = 5 \times 10^{-4}$, and with $10^3$ trajectories sampled from the upstream Gibbs measure $\Gup$.

@@

We now discuss arguably the most novel single result of the manuscript. In the recent theoretical study, \maetal derived an explicit formula for the outgoing wave-field skewness in terms of the system parameters \cite{majda2019}. More specifically, this formula relates the downstream skewness of surface displacement, $\skw(\eta)$, to the change in slope variance, $\var(\eta_x)$. Here, we recap the derivation of this formula and then test the prediction against new, direct experimental measurements.

@@

Inserting \eqref{H3convert} and \eqref{H2convert} into \eqref{H3H2ratio}, and using the definitions of $C_2$ and $C_3$ from \eqref{C3C2}, gives the remarkably explicit formula
\begin{equation}
\label{SkewPred}
\frac{\skwdn(\eta)} {\vardn(\eta_x) - \varup(\eta_x)} = \frac{1}{3} \epsup^{-3} \dratdn^3 
%= \frac{1}{3} \left( \frac{\ddn}{\etastd} \right)^3
\end{equation}
This formula links the skewness of the outgoing wave field to the change in the variance of surface slope. In particular, it predicts their ratio to scale as the {\em inverse cube of wave amplitude}, $\epsup^{-3}$, and the {\em cube of the depth ratio}, $\dratdn^3$. It is a rather unexpected relationship, as it would have been difficult to anticipate that the displacement skewness and slope variance, among all possible variable combinations, are so intimately related.

 % Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/SkewRat.pdf}
\caption{
Experimental confirmation of the explicit formula for outgoing skewness \eqref{SkewPred}.
(a)--(b) Spatial variation of $\skw(\eta)$ and $\var(\eta_x)$ for several different amplitudes. The maximum of $\skw(\eta)$ and the minimum of $\var(\eta_x)$ each occur at a location that is insensitive to amplitude, $x = $15 cm (blue) and -9 cm (green) respectively.
(c) Measurements of the ratio $\skw(\eta) / \Delta \var(\eta_x)$ from 15 different experiments plotted against the dimensionless wave amplitude $\epsup$. For sufficiently large amplitude, the measurements follow the predicted $\epsup^{-3}$ power law closely.
}
\label{SkewRat}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
 %New experimental measurements guided by theory
